How to use replication assignments for teaching integrity in empirical archaeology

### 2019-08-15 README.Rmd
improve the readme to make it more clear what this is, and what to do with it

# Teaching replication in archaeology
<!-- badges: start -->
[![Launch Rstudio Binder](http://mybinder.org/badge.svg)](https://mybinder.org/v2/gh/benmarwick/replicationteachingarchaeology/master?urlpath=rstudio) 
[![Travis-CI Build Status](https://travis-ci.org/benmarwick/teaching-replication-in-archaeology.svg?branch=master)](https://travis-ci.org/benmarwick/teaching-replication-in-archaeology)
[![ORCiD](https://img.shields.io/badge/ORCiD-0000--0001--7879--4531-green.svg)](http://orcid.org/0000-0001-7879-4531)

@@

> Marwick, B., L. Wang, R. Robinson, H. Loiselle (2019). _`r Title`_. Name of journal/book <https://doi.org/10.17605/OSF.IO/DBSW9>

@@

### How to download or install

You can download the compendium as a zip from from this URL: [master.zip](/archive/master.zip)

Or you can install this compendium as an R package, teachingreplicationinarchaeology, from GitHub with:

>>>>

# Teaching replication in archaeology
<!-- badges: start -->
[![Launch Rstudio Binder](http://mybinder.org/badge.svg)](https://mybinder.org/v2/gh/benmarwick/replicationteachingarchaeology/master?urlpath=rstudio) 
[![Travis-CI Build Status](https://travis-ci.org/benmarwick/teaching-replication-in-archaeology.svg?branch=master)](https://travis-ci.org/benmarwick/teaching-replication-in-archaeology)

@@

> Marwick, B. [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7879-4531), L. Wang [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-9060-2125), R. Robinson, H. Loiselle (2019). _`r Title`_. Submitted to _Advances in Archaeological Practice_ <https://doi.org/10.17605/OSF.IO/DBSW9>

@@

### Overview of contents

## Contents

The **analysis** directory contains:

- [:file_folder: paper](/analysis/paper): R Markdown source document for manuscript. Includes code to reproduce the figures and tables generated by the analysis. It also has a rendered version, `paper.docx`, suitable for reading (the code is replaced by figures and tables in this file)    
- [:file_folder: data](/analysis/data): Data used in the analysis.  
- [:file_folder: figures](/analysis/figures): Plots and other illustrations

### How to run in your broswer or download and run locally

The simplest way to explore the text, code and data is to click on [binder](https://mybinder.org/v2/gh/benmarwick/replicationteachingarchaeology/master?urlpath=rstudio) to open an instance of RStudio in your browser, which will have the compendium files ready to work with. Binder uses rocker-project.org Docker images to ensure a consistent and reproducible computational environment. These Docker images can also be used locally.

You can download the compendium as a zip from from this URL: [master.zip](/archive/master.zip). After unzipping, open the `Proj` file in RStudio, and run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the [DESCRIPTION](/DESCRIPTION) file). Then open `paper.Rmd` and knit to produce the `paper.docx`.
